Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-01 body.tex
Tweaks to methods

\noindent
in which
$G$ is the gravitational constant,
$(\phi, \lambda, r)$ are
the latitude, longitude, and radius
coordinates of computation point P (Fig.~\ref{fig:tesseroid}),
$\alpha,\beta \in \{x,y,z\}$
are the local coordinate system of point P,
and

@@

We have opted to use
the 3D Gauss-Legendre Quadrature
to numerically integrate
\ref{eq:tesspot},
\ref{eq:tessgrav},
and
\ref{eq:tesstensor}.
The GLQ
approximates the integral by
a weighted sum
\citep{Hildebrand1987},
e.g.

@@

\noindent
where
$W_i$ are weights and
the discretization points (nodes) $x_i$
are the roots of the $N$th order Legendre polynomial $P_N$
scaled to the integration limits.
The roots of a second-order Legendre polynomial are
$x_1=-0.577350269$ and $x_2=0.577350269$.
For an arbitrary order $N$,
we have used the root-finder algorithm
of \citet{Barrera-Figueroa2006}
to calculate the roots of $P_N$.
The weights $W_i$ are \citep{Hildebrand1987}

>>>>

\noindent
in which
$G$ is the gravitational constant,
$(\phi, \lambda, r)$ are
the latitude, longitude, and radius
coordinates of computation point P (Fig.~\ref{fig:tesseroid}),
$\alpha,\beta \in \{x,y,z\}$
are directions in the local coordinate system of point P,
and

@@

Equations
\ref{eq:tesspot},
\ref{eq:tessgrav},
and
\ref{eq:tesstensor}
can be numerically integrated using
the 3D Gauss-Legendre Quadrature (GLQ)
\citep{Asgharzadeh2007}.
The GLQ
approximates the integral by
a weighted sum
\citep{Hildebrand1987},
e.g.

@@

\noindent
where
$W_i$ are weights and
the discretization points (nodes) $x_i$
are the roots of the $N$th order Legendre polynomial $P_N$.
Note that the roots have to be scaled to the integration limits.
The roots of a second-order Legendre polynomial are
$x_1=-0.577350269$ and $x_2=0.577350269$.
For an arbitrary order $N$,
we have used the root-finder algorithm
of \citet{Barrera-Figueroa2006}
to calculate the roots of $P_N$.
The weights $W_i$ are \citep{Hildebrand1987}
